---
title: "Visualizing quantitative variables"
description: |
  This post shows distribution and relationship of quantitative variables.
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## EDA

### Visualizing distribution of quantitative variables 
Box plots, Histogram & Q-Q plot & Scatter plot

```{r}
library(tidyverse)
library(ggthemes)
library(wesanderson)
```


```{r}
setwd("D:\\setebe\\Data science\\2024\\Tourism\\learning-from-data")
tz <- read.csv("Train.csv")
```

**Box plots**

***Total female***
```{r}
ggplot(tz, aes(total_female)) + 
  geom_boxplot() +
  theme_bw() 

```

***Total male***
```{r}
 
ggplot(tz, aes(total_male)) + 
  geom_boxplot() +
  theme_bw() 
```

***Night spent in mainland***
```{r}

ggplot(tz, aes(night_mainland)) + 
  geom_boxplot() +
  theme_bw() 
```

***Night spent in Zanzibar***
```{r}

ggplot(tz, aes(night_zanzibar)) + 
  geom_boxplot() +
  theme_bw() 
```

**Histogram & Q-Q plot**

***Total female***
```{r}

ggplot(tz, aes(total_female)) + 
  geom_histogram(binwidth=3, fill="red", colour="black") +
  ggtitle("This is Parametric distribution type weibull") +
  theme_bw() 

ggplot(tz, aes( sample = total_female))+ stat_qq()+ 
  stat_qq_line()+ theme_bw() 
```


***Total male***
```{r}
ggplot(tz, aes(total_male)) + 
  geom_histogram(binwidth=3, fill="red", colour="black") +
  ggtitle("This is Parametric distribution type weibull") +
  theme_bw() 

ggplot(tz, aes( sample = total_male))+ stat_qq()+ 
  stat_qq_line()+ theme_bw() 

```


***Night spent in mainland***
```{r}
ggplot(tz, aes(night_mainland)) + 
  geom_histogram(binwidth=10, fill="red", colour="black") +
  ggtitle("This is Parametric distribution type weibull") +
  theme_bw() 

ggplot(tz, aes( sample = night_mainland))+ stat_qq()+ 
  stat_qq_line()+ theme_bw() 

```

***Night spent in Zanzibar***
```{r}
ggplot(tz, aes(night_zanzibar)) + 
  geom_histogram(binwidth=10, fill="red", colour="black") +
  ggtitle("This is Parametric distribution type weibull") +
  theme_bw() 

ggplot(tz, aes( sample = night_zanzibar))+ stat_qq()+ 
  stat_qq_line()+ theme_bw() 
```

### Visualizing relationship of quantitative variables 

**Scatter plot**

***Total female vs Total male***
```{r}

ggplot(tz, aes(total_female, total_male)) + 
  geom_point() +
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE,color = "red") +
  labs(title = "Positive relationship",
       subtitle = "", 
       caption = "",
       x = "Total female",
       y = "Total male") +
  theme_bw() +
  theme(plot.title = element_text(color="black", size=12, 
                                  face="bold",hjust=0),
        plot.subtitle = element_text(color="black", size=10, 
                                     face="bold.italic"),
        plot.caption = element_text(size=10, color="black", 
                                    face="italic",hjust=0.1),
        axis.title.x = element_text(color="black", size=10, 
                                    face="bold"),
        axis.title.y = element_text(color="black", size=10, 
                                    face="bold"),
        axis.text.x = element_text(hjust= 0.5, 
                                   vjust= 0.8, colour="black", 
                                   size=rel(1.2)))

 
```


***Total female vs night mainland***
```{r}
ggplot(tz, aes(total_female, night_mainland)) + 
  geom_point() +
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE,color = "red") +
  labs(title = "Positive relationship",
       subtitle = "", 
       caption = "",
       x = "Total female",
       y = "Night mainland") +
  theme_bw() +
  theme(plot.title = element_text(color="black", size=12, 
                                  face="bold",hjust=0),
        plot.subtitle = element_text(color="black", size=10, 
                                     face="bold.italic"),
        plot.caption = element_text(size=10, color="black", 
                                    face="italic",hjust=0.1),
        axis.title.x = element_text(color="black", size=10, 
                                    face="bold"),
        axis.title.y = element_text(color="black", size=10, 
                                    face="bold"),
        axis.text.x = element_text(hjust= 0.5, 
                                   vjust= 0.8, colour="black", 
                                   size=rel(1.2)))

```


***Total male vs night mainland***
```{r}
ggplot(tz, aes(total_male, night_mainland)) + 
  geom_point() +
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE,color = "red") +
  labs(title = "Negative relationship",
       subtitle = "", 
       caption = "",
       x = "Total male",
       y = "Night mainland") +
  theme_bw() +
  theme(plot.title = element_text(color="black", size=12, 
                                  face="bold",hjust=0),
        plot.subtitle = element_text(color="black", size=10, 
                                     face="bold.italic"),
        plot.caption = element_text(size=10, color="black", 
                                    face="italic",hjust=0.1),
        axis.title.x = element_text(color="black", size=10, 
                                    face="bold"),
        axis.title.y = element_text(color="black", size=10, 
                                    face="bold"),
        axis.text.x = element_text(hjust= 0.5, 
                                   vjust= 0.8, colour="black", 
                                   size=rel(1.2)))


```


***Total female vs night Zanzibar***
```{r}
ggplot(tz, aes(total_female, night_zanzibar)) + 
  geom_point() +
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE,color = "red") +
  labs(title = "Positive relationship",
       subtitle = "", 
       caption = "",
       x = "Total female",
       y = "Night Zanzibar") +
  theme_bw() +
  theme(plot.title = element_text(color="black", size=12, 
                                  face="bold",hjust=0),
        plot.subtitle = element_text(color="black", size=10, 
                                     face="bold.italic"),
        plot.caption = element_text(size=10, color="black", 
                                    face="italic",hjust=0.1),
        axis.title.x = element_text(color="black", size=10, 
                                    face="bold"),
        axis.title.y = element_text(color="black", size=10, 
                                    face="bold"),
        axis.text.x = element_text(hjust= 0.5, 
                                   vjust= 0.8, colour="black", 
                                   size=rel(1.2)))

```

***Total male vs night Zanzibar*** 
```{r}

ggplot(tz, aes(total_female, night_zanzibar)) + 
  geom_point() +
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE,color = "red") +
  labs(title = "Postive relationship",
       subtitle = "", 
       caption = "",
       x = "Total male",
       y = "Night Zanzibar") +
  theme_bw() +
  theme(plot.title = element_text(color="black", size=12, 
                                  face="bold",hjust=0),
        plot.subtitle = element_text(color="black", size=10, 
                                     face="bold.italic"),
        plot.caption = element_text(size=10, color="black", 
                                    face="italic",hjust=0.1),
        axis.title.x = element_text(color="black", size=10, 
                                    face="bold"),
        axis.title.y = element_text(color="black", size=10, 
                                    face="bold"),
        axis.text.x = element_text(hjust= 0.5, 
                                   vjust= 0.8, colour="black", 
                                   size=rel(1.2)))

```


***Night mainland vs night Zanzibar*** 
```{r}

ggplot(tz, aes(night_mainland, night_zanzibar)) + 
  geom_point() +
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE,color = "red") +
  labs(title = "Negative relationship",
       subtitle = "", 
       caption = "",
       x = "Night mainland",
       y = "Night Zanzibar") +
  theme_bw() +
  theme(plot.title = element_text(color="black", size=12, 
                                  face="bold",hjust=0),
        plot.subtitle = element_text(color="black", size=10, 
                                     face="bold.italic"),
        plot.caption = element_text(size=10, color="black", 
                                    face="italic",hjust=0.1),
        axis.title.x = element_text(color="black", size=10, 
                                    face="bold"),
        axis.title.y = element_text(color="black", size=10, 
                                    face="bold"),
        axis.text.x = element_text(hjust= 0.5, 
                                   vjust= 0.8, colour="black", 
                                   size=rel(1.2)))

```

